Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-23 mu/article/article.tex
Almost finishing the corrections.

In the top frames of top and bottom panel of Fig. \ref{fig:up-vab-comp-rtp-1} we
present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
the polarization angle to $\alpha=40^{\circ}$ for which the response is
maximized. In the same panels and frames we present in dashed lines the
corresponding polar $\theta_{a}(\omega,\alpha)$ and azimuthal
$\varphi_{a}(\omega,\alpha)$ spin angles related to the right scale. Also, in
the bottom frames we present the corresponding components
$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and
$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
    \label{fig:up-3d-vvx-2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}
    \label{fig:up-3d-vvy-2}

    \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function of
    the photon energy and polarization angle $\alpha$ for the \emph{up}
    structure. Two local maxima of both responses are localized in the energy
    range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the visible
    radiation range, and for polarization angles between $25^{\circ}$ and
    $50^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
    \label{fig:up-vx-comp-rtp-2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}
    \label{fig:up-vy-comp-rtp-2}

@@

only the polar angle is hold for the peak of the response having a deviation of
$\pm 2^{\circ}$ since the onset to a energy value of 0.106\,eV but the azimuthal
angle changes since the onset to 0.106\,eV from $99^{\circ}$ to $176^{\circ}$.

@@

incoming beam of 0.118\,eV the components of both,

@@

$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ have no change in the spin
polarization direction. Finally, after this energy value both goes to zero.

@@

1.80\,eV to 2.10\,eV, corresponding to the THz and visible radiation, presented

@@

From this figure we have that for the zone between the energy ranges from
1.92\,eV to 1.94\,eV and from 1.96\,eV to 1.98\,eV and for polarization angles
from $30^{\circ}$ to $45^{\circ}$ those two local maxima zones are held.

@@

In the top frames of Figs. \ref{fig:up-vx-comp-rtp-2} and 
\ref{fig:up-vy-comp-rtp-2} we present in solid lines the results of

@@

maximized for the \emph{up} structure. In the same figures and frames we present

@@

$\varphi_{\mathrm{y}}(\omega,\alpha)$) angles related to the right scale. In the
bottom frames of same figures we present the decomposition of the responses in
the three corresponding components $\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.

@@

We found that for both cases, the components have similar contributions and for

@@

$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ having fluctuations but being

@@

$\varphi_{\mathrm{y}}(\omega,\alpha)=56^{\circ}$ having variations of
$\pm5^{\circ}$ for energy variations of $\pm0.01$\,eV and being directed over
the fir Cartesian Quadrant of the $xy$ plane.

@@

intense local maxima with all the components of both responses having similar
contributions and resulting in values of

@@

$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$ being almost constant in the
width of the peak having variations of $\pm1^{\circ}$ for variations in energy
of $\pm0.01$\,eV and being directed downward the third Cartesian Quadrant of the
$xy$ plane.

@@

$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ being almost constant with
variations of $\pm1^{\circ}$ for variations in energy of $\pm1$\,eV and being

@@

Finally we have that for bot energies
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ is more intense than
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ being 4.4 times more intense for
1.932\,eV and 5.0 times more intense for 1.972\,eV. Also all the components of
the responses keep the spin polarization positive till an energy of the incoming
beam equal to 1.954\,eV when the spin polarization changes the direction and
after an energy for the incoming beam equal to 2.05\,eV both responses goes to

@@

\textbf{Alt structure.}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
    \label{fig:alt-3d-vvx}
    \\
    \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}
    \label{fig:alt-3d-vvy}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}
    \label{fig:alt-vx-comp-rtp}
    \\
    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}
    \label{fig:alt-vy-comp-rtp}

@@

% %% Description of ALT |V^{a}| 3D
For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
1.0\,eV, corresponding to the THz radiation, where we found the a local maxima
and the most intense responses for $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$
and $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$. In Fig. \ref{fig:alt-3d-vva} we
present the $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ spectra resulting from
evaluate again Eq. \eqref{eq:vv-mag} using different polarization angles
$\alpha$ in Eq. \eqref{eq:vab} but now for the \emph{alt} structure. We can see
that the onset of the response is when the energy of the incoming light is the
same of the gap energy.
From this picture we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone where the maximum response for both,
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ is held. We also found that the
first peak is obtained when the energy of the incoming beam is 0.720\,eV and
the absolute maximum of the response is obtained when for 0.912\,eV, both for a
polarization angle $\alpha = 145^{\circ}$.
% %% Starting description of ALT |V^{a}|, components and RTP
In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
\ref{fig:alt-vy-comp-rtp} we present in solid lines the results of
the polarization angle to $\alpha=145^{\circ}$ for which the response is
maximized for the \emph{alt} structure. In the same figures and frames we
present ind dashed lines the spin polarization angles related to the right scale
and in the bottom frames the corresponding three components.
Making the analysis for the components and angles when the spin current is
directed in the $x$ direction, corresponding to the Fig.
\ref{fig:alt-vx-comp-rtp}, we found that for the \emph{alt} structure when the
energy of the incoming beam is 0.720\,eV we have similar contributions from all
the components resulting in a response of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=19.4$\,Km/s and polar and azimuthal
spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha)=46^{\circ}$ and
$\varphi_{\mathrm{x}}(\omega,\alpha)=41^{\circ}$ having variations in the range
of the peak but being directed over the first Cartesian Quadrant of the $xy$
plane;
for an energy of 0.912\,eV we have a major contribution from the
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component resulting in a total
response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s and angles
$\theta_{\mathrm{x}}(\omega,\alpha)=154^{\circ}$, and
$\varphi_{\mathrm{x}}(\omega,\alpha)=290^{\circ}$ having variations of
$\pm3^{\circ}$ in for energy variations of $\pm1$\,eV and being directed
downward the fourth Cartesian Quadrant of the $xy$ plane.
Making now the analysis for the components and angles when the spin current is
directed along the $y$ direction, corresponding to the Fig.
\ref{fig:alt-vy-comp-rtp}, we found that when the energy of the incoming beam is
0.720\,eV we have more contribution from the
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component resulting in a response of
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=51.9$\,Km/s and angles
$\theta_{\mathrm{y}}(\omega,\alpha)=141^{\circ}$ and
$\varphi_{\mathrm{y}}(\omega,\alpha)=222^{\circ}$ being the first constant and
the second having variations of $\pm3^{\circ}$ for energy variations of
$\pm0.3$\,eV and being directed downward the third Cartesian Quadrant of the
$xy$ plane.
Then, for the peak centered at 0.912\,eV we have similar contributions of all
the components resulting in a response
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=52.3$\,Km/s being this the absolute
maximum response for the \emph{alt} structure. The corresponding angles are
$\theta_{\mathrm{y}}(\omega,\alpha)=129^{\circ}$ and
$\varphi_{\mathrm{y}}(\omega,\alpha)=229^{\circ}$ being both constant for the
energy range of the peak and being directed downward the third Cartesian
Quadrant of the $xy$ plane.
Finally we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative keeping the same spin polarization since the onset of the response to a
energy of the incoming beam of 0.886\,eV when the response decreases and goes to

>>>>

In the top frames of top and bottom panel of Fig. \ref{fig:up-vab-comp-rtp-1} we
present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
the polarization angle to $\alpha=40^{\circ}$ for which the response is
maximized. In the same panels and frames we present in dashed lines the
corresponding polar $\theta_{a}(\omega,\alpha)$ and azimuthal
$\varphi_{a}(\omega,\alpha)$ spin angles related to the right scale. Also, in
the bottom frames we present the corresponding components
$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and
$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}

    \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function of
    the photon energy and polarization angle $\alpha$ for the \emph{up}
    structure. Two local maxima of both responses are localized in the energy
    range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the visible
    radiation range, and for polarization angles between $25^{\circ}$ and
    $50^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}

@@

only the polar angle is hold at $8^{\circ}$ for the peak of the response having
variations of $\pm 2^{\circ}$ but the azimuthal angle changes from $99^{\circ}$
to $176^{\circ}$ having a value of $133^{\circ}$ for the maximum.

@@

incoming beam of 0.118\,eV the components of both responses,

@@

$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, have no change in the spin
polarization direction. Finally, after this energy value the responses go to

@@

1.80\,eV to 2.10\,eV, corresponding to visible radiation, presented

@@

@@

In the top frames of top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-2}
we present in solid lines the results of

@@

maximized for the \emph{up} structure. In the same panels and frames we present

@@

$\varphi_{\mathrm{y}}(\omega,\alpha)$) angles related to the right scale and  In
the bottom frames the corresponding response components.

@@

We found that for both cases the components have similar contributions for the corresponding response and for

@@

$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin

@@

$\varphi_{\mathrm{y}}(\omega,\alpha)=56^{\circ}$ being  the spin directed over
the first Cartesian Quadrant of the $xy$ plane.

@@

intense local maxima for which all the components have similar contributions for
the corresponding response resulting in values of

@@

$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$ being the spin directed
downward the third Cartesian Quadrant of the $xy$ plane.

@@

$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ and the spin being

@@

Also all the components of the responses keep the spin polarization positive
till an energy of the incoming beam equal to 1.954\,eV when the spin
polarization ad current changes the direction and after an energy for the
incoming beam equal to 2.05\,eV both responses goes to zero.

@@

\textbf{Alt structure.}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
    \\
    \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}
    \\
    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}

@@

% %%%%%%%%%%%%%%%%%
% %% Description of ALT |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
1.0\,eV, corresponding to the NIR radiation, where we found a local maxima and
the most intense responses for $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$; the corresponding spectra is
shown in Fig. \ref{fig:alt-3d-vva}.
%
From this figure we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone where the maximum for both responses is held.
% %%%%%%%%%%%%%%%%
% %% Starting description of ALT |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%
In the top frames of top and bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we
present the spectra of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
the polarization angle to $\alpha=145^{\circ}$. In the same figures and frames
we present the spin polarization angles related to the right scale and in the
bottom frames the corresponding three components.
% 
Making the analysis for the components and angles when the spin current is
directed in the $x$ direction, corresponding to the top panel of Fig.
% 
\ref{fig:alt-vab-comp-rtp}, we found that when the energy of the incoming beam
is 0.720\,eV we have similar contributions from all the components resulting in
a response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=19.4$\,Km/s and polar
and azimuthal spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) =
46^{\circ}$ and $\varphi_{\mathrm{x}}(\omega,\alpha) = 41^{\circ}$ being the
spin directed over the first Cartesian Quadrant of the $xy$ plane;
% 
then, for an energy of 0.912\,eV we have a major contribution from the
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component resulting in a total
response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s being this
value the absolute maximum when the spin velocity is directed in the $x$
Cartesian direction. The corresponding polar and azimuthal angles are
$\theta_{\mathrm{x}}(\omega,\alpha)=154^{\circ}$, and
$\varphi_{\mathrm{x}}(\omega,\alpha)=290^{\circ}$ being the spin directed
downward the fourth Cartesian Quadrant of the $xy$ plane.
% 
Making now the analysis for the components and angles when the spin current is
directed along the $y$ direction, corresponding to the bottom panel of Fig.
\ref{fig:alt-vab-comp-rtp}, we found that when the energy of the incoming beam
is 0.720\,eV we have more contribution from the
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component and the response has a
value of $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 51.9$\,Km/s corresponding
the polar and azimuthal angles $\theta_{\mathrm{y}}(\omega,\alpha) =
141^{\circ}$ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 222^{\circ}$ being the
spin directed downward the third Cartesian Quadrant of the $xy$ plane.
% 
For the peak centered at 0.912\,eV we have similar contributions of all the
components resulting in a response $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| =
52.3$\,Km/s being this the absolute maximum response for the \emph{alt}
structure. The corresponding angles are $\theta_{\mathrm{y}}(\omega,\alpha) =
129^{\circ}$ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 229^{\circ}$ being the
spin directed downward the third Cartesian Quadrant of the $xy$ plane.
% 
Finally we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative keeping the same spin polarization and velocity direction since the
onset of the response to a energy of the incoming beam of 0.886\,eV when the
response decreases and goes to zero.
